Continuous Generalization of Buildings

### 2017-03-14 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
improved the interpretation of our basic idea; removed some unused codes

\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
\usepackage{caption}
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
\usepackage{pdflscape}
%\usepackage{rotating}
\usepackage{afterpage}
%\usepackage[disable]{todonotes}
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
%\usepackage{todonotes}
\usepackage[backend=bibtex,bibstyle=authoryear,citestyle=authoryear,
firstinits=true,doi=false,isbn=false,url=false,eprint=false,dashed=false,natbib=true]{biblatex}
%\renewcommand*{\bibfont}{\small}
\addbibresource{References.bib}
\usepackage{subfigure}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{setspace}
\usepackage{epstopdf}
\usepackage{flafter} %make sure that the floats are not placed 
%before their definition
\usepackage{times}
\usepackage{bm}
\usepackage{gensymb}  % for degree sign, e.g., temperature
\usepackage{amsmath}
\usepackage{amstext}
\usepackage{array}  %for define the fomats of columns in a table
\usepackage{dcolumn}
\usepackage[T1]{fontenc}
\usepackage{pgfplots}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{capt-of}
%\usepackage{marginnote}
\usepackage{xargs}   % Use more than one 
%optional parameter in a new commands
%\usepackage{siunitx} %for scientific 
%notation
%%we do this because of a bug of package floatrow
%\let\tmp\newinsert
%\let\newinsert\newbox
%\usepackage{floatrow}
%\let\newinsert\tmp

\usepackage{verbatimbox}  %for \addvbuffer
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{xspace}
%\usepackage{pdfcomment}
%\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
%		\node[shape=circle,draw,inner sep=1pt] (char) {#1};}}
%\newcommand*\circledtwo[1]{\tikz[baseline=(char.base)]{
%		\node[shape=circle,draw,inner sep=0.1pt] (char) {#1};}}
% \newcommand{\ml}{\ensuremath{M_+}\xspace}
% \newcommand{\ms}{\ensuremath{M_-}\xspace}

@@

@@

Our generalisation is as follows. We buffer buildings with 
radius $\frac{1}{2}d_i+r_i-r_{i-1}$, and merge the buffers 
overlapping 
each 
other.
Then we buffer the results with $-\frac{1}{2}d_i$.
In order to 
remove some spikes from the buffering, we buffer the new results 
with $-\epsilon_i$, and then again with $\epsilon_i$. We simply 
set 
$\epsilon_i=\frac{1}{10}(r_i-r_{i-1})$. After these buffering 
operations, we 
eliminate the buildings with area less than $d^2_i$.

>>>>

\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
\usepackage{caption}
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
\usepackage{pdflscape}
%\usepackage{rotating}
\usepackage{afterpage}
%\usepackage[disable]{todonotes}
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
%\usepackage{todonotes}
\usepackage[backend=bibtex,bibstyle=authoryear,citestyle=authoryear,
firstinits=true,doi=false,isbn=false,url=false,eprint=false,dashed=false,natbib=true]{biblatex}
%\renewcommand*{\bibfont}{\small}
\addbibresource{References.bib}
\usepackage{subfigure}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{setspace}
\usepackage{epstopdf}
\usepackage{flafter} %make sure that the floats are not placed 
%before their definition
\usepackage{times}
\usepackage{bm}
\usepackage{gensymb}  % for degree sign, e.g., temperature
\usepackage{amsmath}
\usepackage{amstext}
\usepackage{array}  %for define the fomats of columns in a table
\usepackage{dcolumn}
\usepackage[T1]{fontenc}
\usepackage{pgfplots}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{capt-of}
%\usepackage{marginnote}
\usepackage{xargs}   % Use more than one 
%optional parameter in a new commands
%\usepackage{siunitx} %for scientific 
%notation
%%we do this because of a bug of package floatrow
%\let\tmp\newinsert
%\let\newinsert\newbox
%\usepackage{floatrow}
%\let\newinsert\tmp
\usepackage{enumitem} %make items indent when using 
%\begin{enumerate}[(a)]
\usepackage{verbatimbox}  %for \addvbuffer
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{xspace}
%\usepackage{pdfcomment}
%\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
%		\node[shape=circle,draw,inner sep=1pt] (char) {#1};}}
%\newcommand*\circledtwo[1]{\tikz[baseline=(char.base)]{
%		\node[shape=circle,draw,inner sep=0.1pt] (char) {#1};}}
% \newcommand{\ml}{\ensuremath{M_+}\xspace}
% \newcommand{\ms}{\ensuremath{M_-}\xspace}

@@

%\pagebreak[4]
%\newpage
\clearpage

@@

Our generalisation is as following $4$ steps:
\begin{enumerate}[label=(\alph*),leftmargin=2\parindent]
	\item We buffer buildings with 
	radius $\frac{1}{2}d_i+r_i-r_{i-1}$, and merge the buffers 
	overlapping each other.
	\item Then we buffer the results with $-\frac{1}{2}d_i$.
	\item In order to 
	remove some spikes from the buffering, we buffer the new 
	results with $-\epsilon_i$.
	\item To compensate, we buffer with $\epsilon_i$.	
\end{enumerate}
We simply set 
$\epsilon_i=\frac{1}{10}(r_i-r_{i-1})$. After these buffering 
operations, we eliminate the buildings with area less than 
$d^2_i$.
